Language-Based Security for Low-Level MPC

### 2024-05-21 ppdp24/intro.tex

Our main focus is on PL design and automated and semi-automated
reasoning about security properties of low-level MPC protocols.  We
consider related systems in several dimensions, including
whether they are aimed at low-level design with probabilistic features,
whether they support reasoning about conditional probabilities which
are central to real/ideal security, whether they consider MPC
security through the lens of hyperproperties, and whether they consider
passive and/or malicious security models. We summarize this comparison
in Figure \ref{fig-comp}, with the caveat that works vary in the degree
of development in each dimension.

Various related low-level languages with probabilistic features have
also been developed. The $\lambda_{\mathrm{obliv}}$ language
\cite{darais2019language} uses a type system is used to automatically
enforce so-called probabilistic trace obliviousness.  But similar to
previous work on oblivious data structures \cite{10.1145/3498713},
obliviousness is related to pure noninterference, not the relaxed form
related to passive MPC security. The Haskell-based security type system in
\cite{6266151} enforces a version of conditioned noninterence that is
sound for passive security in a probabilisitic low-level setting, but
they do not consider malicious security. And properties of real/ideal
passive and malicious security for a probabilistic language have been
formulated in EasyCrypt \cite{8429300}-- though their proof methods,
while mechanized, are fully manual, and their formulation of malicious
security is not as clearly related to robust declassification as is the
one we present in Section \ref{section-hyper}.

@@

>>>>

@@

Our main focus is on PL design and automated and semi-automated
reasoning about security properties of low-level MPC protocols. Prior
work has considered \textbf{automated} verification of
\textbf{high-level} protocols and \textbf{manual} verification of
\textbf{low-level} protocols---but none offers the combination of
automation and low-level support we consider.
%
We summarize this comparison in Figure
\ref{fig-comp}, with the caveat that works vary in the degree of
development in each dimension.

% We consider related systems in several
% dimensions, including whether they are aimed at low-level design with
% probabilistic features, whether they support reasoning about
% conditional probabilities which are central to real/ideal security,
% whether they consider MPC security through the lens of
% hyperproperties, and whether they consider passive and/or malicious
% security models.

Various related low-level languages with probabilistic features have
also been developed. The $\lambda_{\mathrm{obliv}}$ language
\cite{darais2019language} uses a type system is used to automatically
enforce so-called probabilistic trace obliviousness.  But similar to
previous work on oblivious data structures \cite{10.1145/3498713},
obliviousness is related to pure noninterference, not the relaxed form
related to passive MPC security. Similarly, the Haskell-based security type system in
\cite{6266151} enforces a version of noninterence that is
sound for passive security, but does not verify the correctness of declassifications and does not consider malicious security. And properties of real/ideal
passive and malicious security for a probabilistic language have been
formulated in EasyCrypt \cite{8429300}-- though their proof methods,
while mechanized, are fully manual, and their formulation of malicious
security is not as clearly related to robust declassification as is the
one we present in Section \ref{section-hyper}.
